---
title: "R Review"
author: "tsy"
date: "2020/5/4"
output: html_document
---

###(1.)Basic Introduction

 **Calculater**
 
 *Example*
 
```{r}
#加
5 + 3
#乘
5 * 3
#除
5 / 3
#次方
5 ^ 3
#餘數
5 %% 3
#商
5 %/% 3

```

```{r}
##Sequence
1:10
seq(1, 10, 2)
#從第一個開始每兩個取一次
seq(1,10, length.out = 6)
#1~10等差取6個數
```
```{r}
##Assign a names to a value
a <- 3 ^ 5
a
```
```{r}
##Special values
NA
NaN
Inf
pi
1e-3
Inf - Inf + 10
signif(83524, digits = 2)
trunc(125.3333)#去掉小數
```
###Descriptive Stastistics

```{r}
x <- 1:25
mean(x)
var(x)
quantile(x, c(0.1, 0.5, 0.7))
##Create a vector
x <- c(1, 3, 5, 7, 9, 11)
y <- c(2, 4, 6, 8, 10, 12)
x
y
z <- c(1:25, NA)
mean(z, na.rm = TRUE) #要把NA去除
summary(z)
boxplot(z)
objects()   #現在有的變數

```
###Vector

```{r}
##Vectors
v1 <- c(1:5)
v2 <- c(3:6)
length(v1)#vector裡面有幾個元素
v1
v1[1]
v1[-1]#刪除第一個
rep(seq(2, 10, 2), 2)
rep(c(1, 4), c(3, 2))
a <- c(3, 4, 2, 7, 10, 23, 8, 9, 11)
sort(a)#按大小排
order(a)#6(sort之後數字原本的index)

```
```{r}
##Character vectors
text1 <- "Hello R World!!!" 
text1
toupper(text1)
colors <- c("red", "yellow", "BLUE")
more.colors <- c(colors, "green", "cyan")
grep("y", more.colors)#有y元素的index
paste(colors, "line")
f.c <- factor(colors)
#[1] red    yellow BLUE  
#Levels: BLUE red yellow(按字母順序排)
##Logical words
T
F
3 > 5
A <- c(T, T, F, T, F)
!A
sum(A)#有幾個TRUE
is.na(NA)
is.na(2)
c(class(2), class('Hello'), class(TRUE))
```
###排序以及替換
```{r}
a <- c(3, 4, 2, 7, 10, 23, 8, 9, 11)
sort(a)
inc.order <- order(a)
dec.order <- order(a, decreasing = TRUE)
inc.order
dec.order
a[dec.order[3]]
a[c(5, 8)]
a[c(8, 5)]
a[c(5, 8)] <- a[c(8, 5)]
a
a[c(2:7)] <- a[c(7:2)]
a
```
###Control Flow 
```{r}
set.seed(20191025)
X <- sample(1:6,1)
repeat{
  if(length(unique(X))<6){
    X <- c(X,sample(1:6,1))
  }else{
    break
  }
}
length(X)
##Control Flow
set.seed(20191025)
s <- c()
for(i in 1:100){
  s <- c(s,runif(1))
  if(sum(s)>3){
    print(s)
    break
  }
}
```
###費式數列
```{r}
Fib1 <- 1
Fib2 <- 1
Fibonacci <- c(Fib1)
repeat
{
  if(Fib2 >= 100) break
    Fibonacci <- c(Fibonacci, Fib2)
    Fib1 <- Fibonacci[length(Fibonacci) - 1]
    Fib2 <- Fib1 + Fibonacci[length(Fibonacci)]

}
Fibonacci
```
###Matrix
```{r}
A <- c(3, 2, 1, 2, 2, 6, 4, 1, 4, 8, 6, 2, 5, 10, 8, 6, 3, 4, 3, 4)
B <- matrix(A, 4, 5)

A <- matrix(rnorm(1500), 500, 3)
library(rbenchmark)
benchmark(replications=rep(1000, 1),
          apply(A, 1, sum), rowSums(A),
          columns=c('test', 'elapsed', 'relative'))
```
###迴圈
```{r}
a <- 3
b <- 7
if(a == b){
  c <- a*b
  print(c)
}else if(a == 2){
  c <- 4
}else{
  c <- a+b
  print(c)
}

#型式二
if(a == b) c <- a*b

basket <- c("r", "b", "y", "y", "r", "r", "b")
n.r <- 0
n.b <- 0
n.y <- 0
for(i in 1:length(basket)){
  if(basket[i] == "r"){
    n.r <- n.r + 1
  }else if(basket[i] == "b"){
    n.b <- n.b + 1
  }else{
    n.y = n.y + 1
  }
}
ans <- c(n.r, n.b, n.y)
ans

n <- 1
m <- 2
ifelse(n == m, 100, 1)

#ex
v <- c(0.87, -0.47, 0.74, -0.60, -0.23, 0.63, -1.16, -1.08,
       -2.02, 0.26, 0.85, -1.73, 1.12, -1.32, -1.08, -0.95, 
       -1.73, -0.88)
v.min <- v[1]
v.Max <- v[1]
for(i in 1:length(v)){
  if(v.min > v[i]){
    v.min <- v[i]
  }
  if(v.Max < v[i]){
    v.Max <- v[i]  
  }
}
v.Max
v.min
```
* binomial 

```{r}
dbinom(x=3,size=9,prob=0.5)
#cumulative probability(P(X<=3))
pbinom(3,9,0.5)
qbinom(0.76,9,0.5)
```

###ggplot
#需要API Key
library(ggmap)
route_df <- route(from = "Hyderabad, Telangana 500085, India",
                  to = "Kukatpally, Hyderabad, Telangana 500072, India",
                  structure = "route")

my_map <- get_map("Hyderabad, Telangana 500085, India", zoom = 13)

ggmap(my_map) +
  geom_path(aes(x = lon, y = lat), color = "blue", size = 1.5,
            data = route_df, lineend = "round")


trek_df <- trek(from = "Hyderabad, Telangana 500085, India",
                  to = "Kukatpally, Hyderabad, Telangana 500072, India")

my_map <- get_map("Hyderabad, Telangana 500085, India", zoom = 13)

ggmap(my_map) +
  geom_path(aes(x = lon, y = lat), color = "red", size = 1.5,
            data = trek_df, lineend = "round")

## comparison to trek
route_df <- route(from, to, structure = "legs")
qmap("college station, texas", zoom = 8) +
  geom_path(
    aes(x = lon, y = lat),  colour = "red",
    size = 1.5, alpha = .5,
    data = route_df, lineend = "round"
  ) +
  geom_path(
    aes(x = lon, y = lat),  colour = "blue",
    size = 1.5, alpha = .5,
    data = trek_df, lineend = "round"
  )

qmap("college station, texas", zoom = 6) +
  geom_path(
    aes(x = lon, y = lat), colour = "red", size = 1.5,
    data = route_df, lineend = "round"
  )

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1.(1)
Binomial distribution with parameters n and p with x = 0, …, n
$$f(x) = {{n}\choose{x}}\cdot p^x \cdot (1-p)^{n-x},x = 0,...,n$$

1.(2)
Gamma distribution with shape parameter $\alpha$ and the rate parameter with x>0.
$$ f(x) = \frac{x^{\alpha-1} e^{-x/\beta}}{\beta^\alpha \Gamma(\alpha)},\Gamma(\alpha) = \int_{0}^{\infty}{t^{\alpha-1} e^{-t} dt},\alpha,\beta > 0$$


1.(3)
Normal distribution with parameters  and  with −∞ < x < ∞.
$$f(x) = \frac {1}{\sigma {\sqrt {2\pi}}}e^{-\frac {\left(x-\mu \right)^{2}}{2\sigma ^{2}}},−∞ < x < ∞$$
2. Draw the pdf (or pmf) of each distribution in Question 1. 
```{r, fig.width = 10, fig.height = 8}
par(mfrow = c(2,2))

x <- seq(0,10)
n <- 10
k <- seq(0,n)
plot(x,dbinom(k,n,0,7),type = "n",main = title(expression(paste("Binomial(", n , ", ", p, ") with ", n, " = 10"))) ,xlab = "x",ylab = "pmf",xlim = c(0,10),ylim = c(0,0.4))
points(x,dbinom(k,n,0.7),type = "h",lty = 1)
points(x,dbinom(k,n,0.5),type = "h",col = "blue",lty = 4)
points(x,dbinom(k,n,0.2),type = "h",col = "red",lty = 2)
points(x,dbinom(k,n,0.7),type = "p",pch = 19)
points(x,dbinom(k,n,0.5),type = "p",col = "blue",pch = 8)
points(x,dbinom(k,n,0.2),type = "p",col = "red",pch = 17)
legend("topright",c("p = 0.7","p = 0.5","p = 0.2"),col = c(1,"blue",2),lty = c(1,4,2),pch = c(19,8,17),cex = 1)

x <- seq(0,5)
plot(x,dgamma(x,1,3),type = "n",maim = title(expression(paste("Gamma(", alpha , ", ", lambda, ") with ", lambda, " = 3"))),xlab = "x",ylab = "pdf",xlim = c(0,5),ylim = c(0,3))
curve(dgamma(x,1,3),col = 1,lwd = 2,lty = 1,add = TRUE)
curve(dgamma(x,2,3),col = 2,lwd = 2,lty = 2,add = TRUE)
curve(dgamma(x,3,3),col = "blue",lwd = 2,lty = 4,add = TRUE)
curve(dgamma(x,5,3),col = "grey",lwd = 2,lty = 5,add = TRUE)
legend("topright",c("α = 1","α = 2","α = 3","α = 5"),col = c(1,2,"blue","grey"),lty = c(1,2,4,5),cex = 1)

x <- seq(0,20)
plot(x,dnorm(x,5,1),type = "n",maim = title(expression(paste("N(", mu , ", ", sigma^2, ") with ", sigma^2, " = 1"))),xlab = "x",ylab = "pdf",xlim = c(0,20),ylim = c(0,0.4))
curve(dnorm(x,5,1),col = 1,lwd = 2,lty = 1,add = TRUE)
curve(dnorm(x,10,1),col = 2,lwd = 2,lty = 2,add = TRUE)
curve(dnorm(x,12,1),col = "blue",lwd = 2,lty = 4,add = TRUE)
curve(dnorm(x,14,1),col = "grey",lwd = 2,lty = 5,add = TRUE)
legend("topright",c("μ = 5","μ = 10","μ = 12","μ = 14"),col = c(1,2,3,"grey"),lty = c(1,2,4,5),cex = 1)

x <- seq(-10,10)
plot(x,dnorm(x,0,0.5),type = "n",maim = title(expression(paste("N(", mu , ", ", sigma^2, ") with ", mu, " = 0"))),xlab = "x",ylab = "pdf",xlim = c(-9,9),ylim = c(0,0.8))
curve(dnorm(x,0,0.5),col = 1,lwd = 2,lty = 1,add = TRUE)
curve(dnorm(x,0,1),col = 2,lwd = 2,lty = 2,add = TRUE)
curve(dnorm(x,0,2),col = "blue",lwd = 2,lty = 4,add = TRUE)
curve(dnorm(x,0,3),col = "grey",lwd = 2,lty = 5,add = TRUE)
legend("topright",c("σ = 0.5","σ = 1","σ = 2","σ = 3"),col = c(1,2,3,"grey"),lty = c(1,2,4,5),cex = 1)

``` 


